---
title: "Sankey Diagram of Energy Flows in the Netherlands"
author: "Chris Davis"
date: "January 22, 2016"
output: html_document
---

Data sources used:

* [Stroomdiagram energie voor Nederland, 2013](http://www.compendiumvoordeleefomgeving.nl/indicatoren/nl0201-Energiebalans-Nederland-%28stroomdiagram%29.html?i=6-40)
* [Aanbod en verbruik van energiedragers in Nederland, 2013](http://www.compendiumvoordeleefomgeving.nl/indicatoren/nl0053-Energiebalans-Nederland-%28tabel%29.html?i=6-40)

More details can be found at [this blog post](http://blog.ouseful.info/2013/07/23/generating-sankey-diagrams-from-rcharts/).  The most relevant part is the bottom part of the post.  The main idea is that you need to have a CSV spreadsheet
where there are three columns representing the source, target and value of the flow between those two.

TODO:
* Install RStudio
* Figure out how to save Sankey Diagram as png - need to convert svg in webpage somehow
* install base64enc, xlsx

```{r}
#never ever ever convert strings to factors
options(stringsAsFactors = FALSE)

# to install rCharts you must do this once:
#install.packages("devtools")
#require(devtools)
#install_github('ramnathv/rCharts')

library(rCharts)

df = read.csv("NLEnergyFlows.csv")

colnames(df) <- c("source","target","value")
df$source <- as.character(df$source)
df$target <- as.character(df$target)

sankeyPlot <- rCharts$new()
sankeyPlot$setLib('http://timelyportfolio.github.io/rCharts_d3_sankey')

sankeyPlot$set(
  data = df,
  nodeWidth = 10,
  nodePadding = 20,
  layout = 900,
  width = 900,
  height = 400
)
```

```{r SankeyPlot, comment = NA, results = "asis", tidy = F}
# two options for rendering the sankey diagram:
# inline or as an iframe
sankeyPlot$show('inline', include_assets = TRUE, cdn = TRUE)
#sankeyPlot$show('iframesrc', cdn = TRUE)

# save the image as a standalone html file
sankeyPlot$save('StandAloneSankey.html', standalone = TRUE)
```